Multi-state modelling with R: the {\tt msm} package \vskip 0.2in \large{Version <<echo=FALSE,results=tex>>= cat(version) @ \vskip 0.1in <<echo=FALSE,results=tex>>= cat(format(Sys.time(), " @ }

### 2013-12-30 pkg/inst/doc/msm-manual.Rnw
Also remove version detection code, see if that fixes build
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/msm@33 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
Trigger build to test build breakage, and doc typos
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/msm@34 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<echo=FALSE>>=
version <- gsub("Version: +", "",
                packageDescription("msm", lib.loc="../../..")$Version)
@

\title{Multi-state modelling with R: the {\tt msm} package \vskip 0.2in
  \large{Version %
<<echo=FALSE,results=tex>>=
cat(version)
@
\vskip 0.1in
<<echo=FALSE,results=tex>>=
cat(format(Sys.time(), "%d %B, %Y"))
@
}}
\author{Christopher Jackson\\Medical Research Council Biostatistics Unit\\Cambridge, U.K.\\ \texttt{chris.jackson@mrc-bsu.cam.ac.uk}}
\date{}
%% label with date when Rnw is compiled, not when tex is compiled. should be release date of package

>>>>

% version <- gsub("Version: +", "",
%                packageDescription("msm", lib.loc="../../..")$Version)

<<echo=FALSE>>=
version <- 1.3
@

\title{Multi-state modelling with R: the {\tt msm} package \vskip 0.2in
  \large{Version %
<<echo=FALSE,results=tex>>=
cat(version)
@
\vskip 0.1in
<<echo=FALSE,results=tex>>=
cat(format(Sys.time(), "%d %B, %Y"))
@
}}
\author{Christopher Jackson\\MRC Biostatistics Unit\\Cambridge, U.K.\\ \texttt{chris.jackson@mrc-bsu.cam.ac.uk}}
\date{}
%% label with date when Rnw is compiled, not when tex is compiled. should be release date of package
